### 2016-09-08 response.md

ATTACH: Figure from https://cloud.githubusercontent.com/assets/2357126/17576650/cfc59fbe-5f29-11e6-99b7-c39a43c013b6.png

-----------------------------------
Minor Comment 2
-----------------------------------

***2) Figure 6: the authors should comment (unless I missed the comment) on why the bivariate distribution of the FERENGI galaxies in (mu,z) does not match the bivariate distribution for the main sample.***

The FERENGI sample is biased in including examples of galaxies that have lower surface brightnesses than any images found in the real Hubble data, simply because the local Universe has no examples of galaxies at the high surface brightness end. This is a combination of both a finite-volume sample at low redshift in addition to some evolution in the stellar populations and size-magnitude relation over cosmic time.  We deal with this issue partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample that spans (but does not reproduce) the surface brightness-redshift distribution of the real data. The mismatch does not affect the overall calibration accuracy as we are not correcting the population as a whole, but only galaxies at particular bins of surface brightness and redshift.

### 2016-09-08 response.md

The authors agree with the referee that a more typical statistical range would be appropriate. We have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data. The figure (now Figure 8) has been modified and text added to the end of Section 4.1.

----------------------------------
Minor Comment 10
----------------------------------

***10) Section 4.3: "The goodness-of-fit was evaluated in each bin, for each Task, using a normalized chi^2 metric." The authors need to provide the formula for this; the numbers don't make sense, if one assumes "normalized" is the same
as "reduced chi^2" (where the typical value for a good fit is approximately 1).***

We agree that the normalized chi-squared is not the ideal metric for evaluating the goodness-of-fit here. Rather than comparing the fits of the polynomials for Task 1 vs the rest of the tasks, we compare the available data per bin. For Task 1, an average of 59 points were fit in each z-mu bin (now Figure 7). Fitting parameters for any other task is significantly limited by the number of galaxies in each z-mu bin; the higher-order tasks have an average of only 9 galaxies per bin. This is driven by the fact that the tasks do not meet the minimum threshold of 10 individual classifications (this threshold is exceeded for every galaxy in Task 1, however). This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 1.
